---
title: "Decision Tree"
output: html_notebook
---
# Introduction to My First R Notebook
This R-Markdown notebook will focus on Decision Trees, which are a graphical representation of a series of logical decisions, or questions and answers at each stage. They make a useful visual for breaking down a project into different phases, or split decisions to arrive at the overall destination or output.

Starting off with the root node there are 2 branches (bools) and where there is a new question a new node is created each time. Otherwise the branches just result in leafs where they end. Therefore, a top-level node is the root and the bottom-level nodes are leafs. Each decision level is considered to be a 'classification rule'.

A decision tree with categories is called a 'classification tree' and a decision tree with predicted numerical values is called a 'regression tree'. Below I use an example of constructing a decision tree using the rpart ( ) recursive partitioning function.

```{r}
library(rpart)

iris.tree <- rpart(species ~ sepal.length + sepal.width + petal.length + petal.width, iris.uci, method="class")
```
First it is necessary to import the iris dataset from the UCI ML repository.
```{r}
iris.uci <- read.csv("http://archive.ics.uci.edu/ml/machine-learning-databases/iris/iris.data", header=FALSE,
                     col.names=
                       c("sepal.length","sepal.width","petal.length","petal.width","species"))
head(iris.uci)
```

